### 2020-11-12 thesis/thesis.tex
fix maxname
test fix
small fixes
try to fix bibliography
try fix bib again
fix crosby ref

% Bib style
%\setcitestyle{authoryear,open={((},close={))}}
  \usepackage[
    style=apa,
    %maxnames = 2,
    backend=biber,
    natbib=true %, 
    %refsection=chapter
  ]{biblatex}

@@

Connectivity is a pillar of spatial ecology, the study of how ecological dynamics and interactions are structured in space. Connectivity is well known to influence various aspects of populations and community ecology, including dispersal, demographic rescue, and the spread of diseases \citep{krosby_ecological_2010-1, crook_human_2015}. In conservation, connectivity is seen as a landscape feature that can be protected and restored to counteract the effects of  land use and climate change, and ensure the persistence of species in a landscape \citep{costanza_landscape_2019}. \\

@@

This thesis makes use of circuit theory to estimate change to potential functional connectivity for 5 umbrella species, under a certain number of land use change scenarios. Here we use the term "umbrella species", not in its usual meaning, but to designate species whose connectivity needs have been shown to be representative of the needs of a larger pool of 14 species (see \cite{albert_applying_2017, meurant_selecting_2018}). See table \ref{tab:species} for a detailed description of the 5 species. Next, we introduce the study region on which we carry these analyses. \\ \vspace{2em}

>>>>

% Bib style
%\setcitestyle{authoryear,open={((},close={))}}
  \usepackage[
    style=apa,
    maxbibnames=20,
    maxcitenames=2,
    minbibnames=19,
    mincitenames=1,
    isbn = false,
    backend=biber,
    uniquelist = false,
    natbib=true %, 
    %refsection=chapter
  ]{biblatex}

@@

Connectivity is a pillar of spatial ecology, the study of how ecological dynamics and interactions are structured in space. Connectivity is well known to influence various aspects of populations and community ecology, including dispersal, demographic rescue, and the spread of diseases \citep{krosby_ecological_2010, crook_human_2015}. In conservation, connectivity is seen as a landscape feature that can be protected and restored to counteract the effects of  land use and climate change, and ensure the persistence of species in a landscape \citep{costanza_landscape_2019}. \\

@@

This thesis makes use of circuit theory to estimate change to potential functional connectivity for 5 umbrella species, under a certain number of land use change scenarios. Here we use the term "umbrella species", not in its usual meaning, but to designate species whose connectivity needs have been shown to be representative of the needs of a larger pool of 14 species (see \cite{albert_applying_2017, meurant_selecting_2018}). Next, we introduce the study region on which we carry these analyses. \\ \vspace{2em}
